Modeling vertical-axis cross-flow turbine wakes

### 2015-03-20 paper.tex
Add description of turbulence models chosen

>>>>

The flow field was modeled using the Reynolds-averaged Navier--Stokes equations,
employing two different turbulence models--Menter's $k$--$\omega$ SST
\cite{Menter1994} and the Spalart--Allmaras one equation model
\cite{Spalart1992}. The SST model was chosen due to its prominence in the
literature for simulating separating flows, which we assumed to be present in
the current problem in the form of dynamic stall. The Spalart--Allmaras model
was shown by Ferreira et al. \cite{Ferreira2007} to match experimental particle
image velocimetry (PIV) results for a CFT in dynamic stall, though this was a
somewhat low Reynolds number case ($5 \times 10^4$).
